---
title: Development of an Intended Bifactor Engagement Measure
author:
  - name: Morgan Russell
    affil: 1
  - name: Renata Garcia Prieto Palacios Roji, MA
    affil: 1
  - name: Casey Osorio-Duffoo, MA
    affil: 2
  - name: John Kulas, PhD
    affil: 1
affiliation:
  - num: 1
    address: Montclair State University
  - num: 2
    address: Harver
column_numbers: 3
primary_colour: "#640d14"
secondary_colour: "#ad2831"
accent_colour: "#38040e"
#csl: "apa7.csl" # NEED TO FIX THIS
logoright_name: https&#58;//raw.githubusercontent.com/Morgan-Russell/SIOP-2022-poster/main/hawk-logo-white.svg
logoleft_name: https&#58;//raw.githubusercontent.com/Morgan-Russell/SIOP-2022-poster/main/MSU_logo_white.webp
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r warning=FALSE, message=FALSE, echo=FALSE}
# Packages
library(tidyverse)
library(DT)
library(labourR)
library(apaTables)
library(kableExtra)
library(knitr)
```


# Introduction

In recent years, employee engagement has earned its stripes as a useful predictor of employee outcomes (e.g., Hanaysha, 2016; Alarcon & Edwards, 2011; Rich et al., 2010). Despite engagement's burgeoning popularity and emergence into the cultural mainstream, considerable disagreement exists among psychologists on the definition and factor structure of the construct.

The "substantive" model of engagement describes it in terms of three dimensions: Vigor, or high levels of energy at work; Dedication, or feelings of involvement, pride, and meaning in one's work; and Absorption, or concentration and flow while working (Schaufeli et al., 2002). On the other hand, the now-resurgent tripartite model of attitudes (Rosenberg, 1960) divides attitudes into cognitive, affective, and behavioral components.

A traditional scale development approach would generate items which correspond to one 

We sought to develop an instrument which not only would assess both 

Rather than reject one model in favor of the other, we sought to develop an engagement measure in which each item simultaneously captures *both*. 

In so doing, we hope to effectively double the content domain coverage of our scale while minimizing 

# Methods

50 items were generated to semantically reflect one dimension each from the substantive and attitudinal models. For example, "I speak positively about this organization to others" indicates both the dedication and behavioral dimensions from the substantive and attitudinal models respectively. Graduate students and faculty sorted each item twice to their corresponding dimension within the substantive and attitudinal models. The 36 items that were most consistently sorted were retained for the study. 330 working adult participants were gathered via snowball sampling and responded to this set of items.

## Item Reduction

Our team used two parallel scale development methods: one focusing on corrected item-total correlations, the other focusing on CFA modification indices. In the former approach, the item with the lowest corrected item-total correlation was removed from the scale definition. This process was iterated     after each item deletion until only two items per each of the nine pairs of substantive and attitudinal dimensions remained. 

The CFA modification index approach focused on item retention rather than deletion. We ran two parallel CFAs, one on the substantive model and the other on the attituinal model. We prioritized the alternative model predicted model associations as items to retain.

The two parallel item reduction approaches yielded two very similar, yet distinct, 18-item scale definitions. We merged these scales into a final 20-item scale definition based on wording preference and maximizing content domain coverage.

Using the `semplot` package,

```{r items, warning=FALSE, message=FALSE, echo=FALSE}
items <- read.csv("items.csv")

#get kable to shade every other row somehow

knitr::kable(
  items, format = "html",
  caption = "Final 20-item scale definition",
  align = "l",
  escape = FALSE,
  col.names = c("Substantive", "Attitudinal", "Corrected item-total correlation")) %>% kable_styling(bootstrap_options=c("striped", "condensed"))
```


# Results

Table \@ref(tab:items) shows the final set of 20 items.


```{r data, warning=FALSE, message=FALSE, echo=FALSE}





temp <- read.csv("qualtrics_pilot_data.csv", header=FALSE, na.strings="")

x <- temp[2,]
data <- temp[-c(1:3),]
colnames(data) <- x

num <- nrow(data)

## getting conditions into one large file below - 12/9/20

data$Cond1 <- rowSums(is.na(data[18:53]))
data$Cond2 <- rowSums(is.na(data[54:89]))
data$Cond3 <- rowSums(is.na(data[90:125]))
data$Cond4 <- rowSums(is.na(data[126:161]))

data$Condition[data$Cond1 < 36] <- 1
data$Condition[data$Cond2 < 36] <- 2
data$Condition[data$Cond3 < 36] <- 3
data$Condition[data$Cond4 < 36] <- 4

cond1 <- data[ which(data$Condition==1), ]
cond2 <- data[ which(data$Condition==2), ]
cond3 <- data[ which(data$Condition==3), ]
cond4 <- data[ which(data$Condition==4), ]

cond1.red <- cond1[,c(6, 18:53, 162:165, 171)]  ## using Cond1 ordering
cond2.red <- cond2[,c(6, 62:65, 70:73, 82:85, 58:61, 74:77, 86:89, 66:69, 78:81, 54:57, 162:165, 171)]
cond3.red <- cond3[,c(6, 94:97, 106:109, 118:121, 98:101, 110:113, 122:125, 102:105, 114:117, 90:93, 162:165, 171)]
cond4.red <- cond4[,c(6, 138:161, 130:137, 126:129, 162:165, 171)]        ## 171 versus 172 because testing script has extra "hours" variable

names(cond1.red) = gsub(pattern = "C*.* - ", replacement = "", x = names(cond1.red))      ## Getting rid of condition markers so rbind will work
names(cond2.red) = gsub(pattern = "C*.* - ", replacement = "", x = names(cond2.red))  
names(cond3.red) = gsub(pattern = "C*.* - ", replacement = "", x = names(cond3.red))  
names(cond4.red) = gsub(pattern = "C*.* - ", replacement = "", x = names(cond4.red))  

together <- rbind(cond1.red, cond2.red, cond3.red, cond4.red)        ## we'll be using this object for analyses

num_valid <- nrow(together)

i <- c(1:37)                                          ## Changing item responses to numerics
together[ , i] <- apply(together[ , i], 2,            # Specify own function within apply
                        function(x) as.numeric(as.character(x)))


##########################################################
##########################################################
##########################################################
############# RECODES

together$`Most days, I feel happiest when the workday is soon to be complete.` <- 7 - together$`Most days, I feel happiest when the workday is soon to be complete.`
together$`This job drains my energy.` <- 7 - together$`This job drains my energy.`

## BEHAVIORAL (NONE):

## COGNITIVE: 

together$`Thinking about work saps my energy.` <- 7 - together$`Thinking about work saps my energy.`
together$`I often think about finding another job.` <- 7 - together$`I often think about finding another job.`

```

```{r cfa, width="100%", message=FALSE, warning=FALSE, echo=FALSE}

library(lavaan)
library(sem)
library(semPlot)
library(dplyr)


CFAdata<-together[,2:37]

CFAdata<-CFAdata%>%rename(
  Item_1=`I’m able to concentrate on my work without distractions.`,
  Item_2=`I have a hard time detaching mentally from my work.`,
  Item_3=`Time passes quickly while I’m working.`,
  Item_4=`I find it difficult to mentally disconnect from work.`,
  Item_5=`I enjoy thinking about work even when I’m not at work.`,
  Item_6=`Most days, I feel happiest when the workday is soon to be complete.`,
  Item_7=`I am happiest when I am immersed in a project.`,
  Item_8=`I love starting my workday.`,
  Item_9=`I devote more time than is expected of me.`,
  Item_10=`I have to be reminded to take breaks while I’m at work.`,
  Item_11=`I never miss a work deadline.`,
  Item_12=`I never allow distractions to interfere with my work.`,
  Item_13=`I devote my full attention to my work tasks throughout the day.`,
  Item_14=`Thinking about work saps my energy.`,
  Item_15=`I would rather direct my focus toward a work task than a personal task.`,
  Item_16=`I’m able to maintain good levels of energy throughout the workday.`,
  Item_17=`I enjoy spending time completing my job tasks.`,
  Item_18=`Most days I feel enthusiastic about starting my work day.`,
  Item_19=`I feel motivated to go beyond what is asked of me.`,
  Item_20=`This job drains my energy.`,
  Item_21=`When work is slow I find ways to be productive.`,
  Item_22=`I express enthusiasm for my job while at work.`,
  Item_23=`I try my best to perform well at work.`,
  Item_24=`If I notice my energy level is low, I take corrective steps to re-energize.`,
  Item_25=`I plan my future with this company.`,
  Item_26=`I believe this company cares about my career goals.`,
  Item_27=`I often think about finding another job.`,
  Item_28=`This organization challenges me to work at my full potential.`,
  Item_29=`I am proud to be a member of this organization.`,
  Item_30=`I feel supported by my supervisor when I fail at a task.`,
  Item_31=`I feel proud of my accomplishments within this organization.`,
  Item_32=`My job makes me feel like I’m part of something meaningful.`,
  Item_33=`I make valued contributions to the organization.`,
  Item_34=`I embrace challenging situations at work.`,
  Item_35=`I speak positively about this organization to others.`,
  Item_36=`This organization provides the resources necessary for me to successfully perform my job.`
)

modified2 <-'
Absorption = ~Item_1 + Item_3  + Item_5  + Item_8  + Item_10 + Item_11
Vigor      = ~Item_14 + Item_16 + Item_17 + Item_19 + Item_21 + Item_22
Dedication = ~ Item_26 + Item_28 + Item_31 + Item_32 + Item_34 + Item_35
Cognitive  = ~Item_1  + Item_3  + Item_14 + Item_16 + Item_26 + Item_28
Affective  = ~Item_5 +  Item_8  + Item_17 + Item_19 + Item_31 + Item_32
Behavioral = ~Item_10 + Item_11 + Item_21 + Item_22 + Item_34 + Item_35
Absorption ~~ 0*Affective
Absorption ~~ 0*Behavioral
Absorption ~~ 0*Cognitive
Vigor      ~~ 0*Affective
Vigor      ~~ 0*Behavioral
Vigor      ~~ 0*Cognitive
Dedication ~~ 0*Affective
Dedication ~~ 0*Behavioral
Dedication ~~ 0*Cognitive
'

Fit.mod2 <- lavaan::cfa(modified2, data = CFAdata, missing = "ML", estimator = 'MLR')

# semPlot::semPaths(Fit.mod2, bifactor = c("Cognitive", "Affective", "Behavioral"), "std", layout = "tree3",
#                  rotation = 2, curvePivot=TRUE, style="lisrel", nCharNodes = 0, pastel=FALSE)

semPlot::semPaths(Fit.mod2, bifactor = c("Cognitive", "Affective", "Behavioral"), style="lisrel", "std", layout = "tree3", sizeLat=10, rotation = 2, sizeMan=4.5,edge.label.cex=0.75, edge.color="black", asize=2, sizeInt = 0, mar = c(.7,-3,.7,-3))

```

```{r warning=FALSE, message=FALSE, echo=FALSE}
library(ellipse)
library(hexbin)
my.plotcorr <- function (corr, outline = FALSE, col = "grey", upper.panel = c("ellipse", "number", "none"), lower.panel = c("ellipse", "number", "none"), diag = c("none", "ellipse", "number"), digits = 2, bty = "n", axes = FALSE, xlab = "", ylab = "", asp = 1, cex.lab = par("cex.lab"), cex = 0.75 * par("cex"), mar = 0.1 + c(2, 2, 4, 2), ...)
{
# this is a modified version of the plotcorr function from the ellipse package
# this prints numbers and ellipses on the same plot but upper.panel and lower.panel changes what is displayed
# diag now specifies what to put in the diagonal (numbers, ellipses, nothing)
# digits specifies the number of digits after the . to round to
# unlike the original, this function will always print x_i by x_i correlation rather than being able to drop it
# modified by Esteban Buz
  if (!require('ellipse', quietly = TRUE, character = TRUE)) {
    stop("Need the ellipse library")
  }
  savepar <- par(pty = "s", mar = mar)
  on.exit(par(savepar))
  if (is.null(corr))
    return(invisible())
  if ((!is.matrix(corr)) || (round(min(corr, na.rm = TRUE), 6) < -1) || (round(max(corr, na.rm = TRUE), 6) > 1))
    stop("Need a correlation matrix")
  plot.new()
  par(new = TRUE)
  rowdim <- dim(corr)[1]
  coldim <- dim(corr)[2]
  rowlabs <- dimnames(corr)[[1]]
  collabs <- dimnames(corr)[[2]]
  if (is.null(rowlabs))
    rowlabs <- 1:rowdim
  if (is.null(collabs))
    collabs <- 1:coldim
  rowlabs <- as.character(rowlabs)
  collabs <- as.character(collabs)
  col <- rep(col, length = length(corr))
  dim(col) <- dim(corr)
  upper.panel <- match.arg(upper.panel)
  lower.panel <- match.arg(lower.panel)
  diag <- match.arg(diag)
  cols <- 1:coldim
  rows <- 1:rowdim
  maxdim <- max(length(rows), length(cols))
  plt <- par("plt")
  xlabwidth <- max(strwidth(rowlabs[rows], units = "figure", cex = cex.lab))/(plt[2] - plt[1])
  xlabwidth <- xlabwidth * maxdim/(1 - xlabwidth)
  ylabwidth <- max(strwidth(collabs[cols], units = "figure", cex = cex.lab))/(plt[4] - plt[3])
  ylabwidth <- ylabwidth * maxdim/(1 - ylabwidth)
  plot(c(-xlabwidth - 0.5, maxdim + 0.5), c(0.5, maxdim + 1 + ylabwidth), type = "n", bty = bty, axes = axes, xlab = "", ylab = "", asp = asp, cex.lab = cex.lab, ...)
  text(rep(0, length(rows)), length(rows):1, labels = rowlabs[rows], adj = 1, cex = cex.lab)
  text(cols, rep(length(rows) + 1, length(cols)), labels = collabs[cols], srt = 90, adj = 0, cex = cex.lab)
  mtext(xlab, 1, 0)
  mtext(ylab, 2, 0)
  mat <- diag(c(1, 1))
  plotcorrInternal <- function() {
    if (i == j){ #diag behavior
      if (diag == 'none'){
        return()
      } else if (diag == 'number'){
        text(j + 0.3, length(rows) + 1 - i, round(corr[i, j], digits=digits), adj = 1, cex = cex)
      } else if (diag == 'ellipse') {
        mat[1, 2] <- corr[i, j]
        mat[2, 1] <- mat[1, 2]
        ell <- ellipse(mat, t = 0.43)
        ell[, 1] <- ell[, 1] + j
        ell[, 2] <- ell[, 2] + length(rows) + 1 - i
        polygon(ell, col = col[i, j])
        if (outline)
          lines(ell)
      }
    } else if (i >= j){ #lower half of plot
      if (lower.panel == 'ellipse') { #check if ellipses should go here
        mat[1, 2] <- corr[i, j]
        mat[2, 1] <- mat[1, 2]
        ell <- ellipse(mat, t = 0.43)
        ell[, 1] <- ell[, 1] + j
        ell[, 2] <- ell[, 2] + length(rows) + 1 - i
        polygon(ell, col = col[i, j])
        if (outline)
          lines(ell)
      } else if (lower.panel == 'number') { #check if ellipses should go here
        text(j + 0.3, length(rows) + 1 - i, round(corr[i, j], digits=digits), adj = 1, cex = cex)
      } else {
        return()
      }
    } else { #upper half of plot
      if (upper.panel == 'ellipse') { #check if ellipses should go here
        mat[1, 2] <- corr[i, j]
        mat[2, 1] <- mat[1, 2]
        ell <- ellipse(mat, t = 0.43)
        ell[, 1] <- ell[, 1] + j
        ell[, 2] <- ell[, 2] + length(rows) + 1 - i
        polygon(ell, col = col[i, j])
        if (outline)
          lines(ell)
      } else if (upper.panel == 'number') { #check if ellipses should go here
        text(j + 0.3, length(rows) + 1 - i, round(corr[i, j], digits=digits), adj = 1, cex = cex)
      } else {
        return()
      }
    }
  }
  for (i in 1:dim(corr)[1]) {
    for (j in 1:dim(corr)[2]) {
      plotcorrInternal()
    }
  }
  invisible()
}

corr.mtcars <- cor(mtcars)
colors = BTC(100)
colors <- colorRampPalette(c("red", "white", "blue"))(100)
#my.plotcorr(corr.mtcars, col=colors[((corr.mtcars + 1)/2) * 100], diag='ellipse', lower.panel="number", main='Predictor correlations')

corr.cfadata <- cor(CFAdata, use = "complete.obs")

#my.plotcorr(corr.cfadata, col=colors[((corr.cfadata + 1)/2) * 100], diag='ellipse', lower.panel="number", main='Predictor correlations')
```


# Discussion

The persent research introduces a novel measure of engagement, developed in English and available for free. By designing items to correspond to two separate factor structures, we effectively double our content domain coverage with the same number of items. Most novelly, we intentionally embrace complexity in scale development. We believe this approach has promising implications for developing constructs which reconcile, rather than reject, conflicting models of constructs. It it our hope that future researchers will weigh the benefits of broadening content domain coverage over the understandable desire for item parsimony. 

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```

::: {#refs custom-style="Bibliography"}
:::












